{\fontfamily{ptm}\selectfont Lorum ipsum}

### 2025-07-02 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

>>>>

            For one step, a specific function $F_{I_k}$ is sampled. 
            $F_{I_k}$ is $K^{(I_k)} > \mu^{(I_k)} \ge 0$ strongly convex and smooth. 
            The iterates $x_k, v_k$ is a function of random variable $I_k$, conditioned on all $I_{k - 1}, I_{k - 2}, \ldots , I_0$
            The sequence $\alpha_k$ is a sequence of random variable and, the relations between $\alpha_k, \alpha_{k - 1}$ is given by: 
                \alpha_k &= 
                    -\frac{L_{k - 1}\alpha_{k - 1}^2}{L_k} + \frac{\mu^{(I_k)}}{L_k} 
                    + \sqrt{
                            \frac{\mu^{(I_k)}}{L_k}
                            - \frac{\alpha_{k - 1}^2L_{k - 1}}{L_k}
                        \right)^2
                        + \frac{\alpha_{k - 1}4L_{k - 1}}{L_k}
            The relationship $(L_{k - 1}/L_k)(1 - \alpha_k)\alpha_{k - 1}^2 = \alpha_k(\alpha_k - \mu^{(I_k)}/L_k)$ is an instance of Definition \ref{def:rwapg-seq} where $\rho_{k - 1} = L_{k - 1}/L_k$. 
            Therefore, the one-step convergence result of \ref{thm:onestep-napg-cnvg} applies to function $F_{I_k}$ with sequence $\alpha_k$ and, it yields: 
                & - F_{I_k}(\bar x) + F_{I_k}(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                & \le 
                    F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
            We take the conditional expectation on the LHS and, it has 
                & \mathbb E_k 
                \left[
                    - F_{I_k}(\bar x) + F_{I_k}(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \right]
                \mathbb E_k \left[- F_{I_k}(\bar x)\right]
                \mathbb E_k \left[F_{I_k}(x_k)\right]
                \mathbb E_k \left[
                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \right]
                &\underset{\text{(a)}}{=} 
                - F(\bar x) + 
                \mathbb E_k \left[
                    F_{I_k}(x_k)
                \right]
                + \mathbb E_k
                \left[
                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \right]. 
            At label (a), we make use of interpolation hypothesis which makes $\mathbb E_k[F_{I_k}(\bar x)] = F(\bar x)$. 
            Next, taking the conditional expectation on the RHS it has 
                & \mathbb E_k\left[
                    (1 - \alpha_k)
                    F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
                \right]
                &\underset{\text{(b)}}{=}
                \mathbb E_k\left[1 - \alpha_k\right]
                \mathbb E_k
                    \left[
                        F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
                    \right]
                &\neq 
                \mathbb E_k
                \left[1 - \alpha_k\right]
                \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] - F(\bar x)
                    \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2\right]
            At (b), we need to make use of covariance between the two random variable... 
            Consider random variables $X_k = (1 - \alpha_k)$ and $Y_k = F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \alpha_{k - 1}L_{k - 1}/2\Vert \bar x - v_{k - 1}\Vert^2$ which are functions of $I_k$ conditioned on $\alpha_{k - 1}$ and, $x_{k - 1}, v_{k - 1}$. 
            The conditional expectation of their product has $\mathbb E_k[X_kY_k] = \mathbb E_k[X_k] \mathbb E_k[Y_k] + \cov[X_k, Y_k]$.
            \textcolor{red}{Hence, taking the expectation doesn't follow. }

        \begin{definition}[SNAPG-V2]\label{def:snapg-v2}
            Let $F$ satisfies Assumption \ref{ass:sum-of-many}. 
            Let $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$. 
            Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
            The SNAPG generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
            \begin{align*}
                & (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right), \\
                & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
                & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
                & x_k =  T_{L_k}(y_k | F_{I_k}) \text{ s.t: } D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
            \end{align*}
        \end{definition}

        \begin{theorem}[SNAPG-V2 one step convergence]
            Let's suppose that $I_k = i$ and, for all $k \ge 0$ let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ where $\bar x$ is a minimizer of $F$. 
                \item[(a)] We can use proximal gradient inequality from Theorem \ref{thm:pg-ineq} with $z = z_k$ because each $F_i$ is $K_i$ Lipschitz smooth and, $\mu^{(i)}$ strongly convex with $K_i \ge \mu^{(i)}$. 
                \item[(b)] We can use Jesen's inequality of Theorem \ref{thm:jesen} with $z = z_k$ on $F_i$. 
                \item[(c)] The sequence $(\alpha_k)_{k \ge 0}$ has $(L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right)$. It is a special case of Definition \ref{def:rwapg-seq} with $\rho_{k - 1} = L_{k - 1}/L_k$. 
            % INTERMEDIATE RESULTS
            From Definiton \ref{def:snapg-v2}, it has
                    1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
                    \frac{L_k\alpha_k - \mu^{(i)} + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
                = \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}. 
            Therefore, for all $k \ge 0$ $y_k$ has 
                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} 
                    v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}} x_{k - 1}
                \right) - y_k
                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1}
                + \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1} - y_k
                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
                    \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} - (1 - \alpha_k)
                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
                    \frac{L_k - L_k + \mu^{(i)}}{L_k - \mu^{(i)}}
                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
                \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}x_{k - 1} - y_k. 
            Therefore, we establish the equality 
                (1 - \alpha_k)x_{k - 1} - y_k &= 
                - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
                - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}. 
            Using the above, we have 
                z_k - y_k &= 
                \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
                &= \alpha_k \bar x 
                - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
                - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
                    \alpha_k - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}
                \right)\bar x
                - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
                    \frac{\alpha_kL_k - \alpha_k \mu^{(i)} - L_k\alpha_k + \mu^{(i)}}{L_k - \mu^{(i)}}
                \right)\bar x
                - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
                + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}\bar x
                - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
                + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
            % INTERMEDIATE RESULTS
            From Definition \ref{def:snapg-v2} it has directly: 
            % INTERMEDIATE RESULTS
            The proof is direct algebra and it has: 
            {\small\allowdisplaybreaks
                & \frac{\left(\mu^{(i)}\right)^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} 
                - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
                \frac{1}{2\left(L_k - \mu^{(i)}\right)}
                    \left(\mu^{(i)}\right)^2(1 - \alpha_k)^2
                    - \left(L_k - \mu^{(i)}\right)\mu^{(i)} \alpha_k(1 - \alpha_k)
                &= \frac{1 - \alpha_k}{2\left(L_k - \mu^{(i)}\right)}\left(
                    \left(\mu^{(i)}\right)^2 
                    - \left(\mu^{(i)}\right)^2\alpha_k 
                    - \left(L_k \mu^{(i)} \alpha_k - \left(\mu^{(i)}\right)^2 \alpha_k\right)
                    \left(\mu^{(i)}\right)^2 - L_k\left(\mu^{(i)}\right)\alpha_k
                \frac{(1 - \alpha_k)\mu^{(i)}\left(\mu^{(i)} - L_k\alpha_k\right)}
                {2\left(L_k - \mu^{(i)}\right)}
                &= \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
                {2\left(L_k - \mu^{(i)}\right)}. 
            % INTERMEDIATE RESULTS 
            From the property of the sequence stated in item (c), we have: 
                &\frac{\left(
                    L_k\alpha_k - \mu^{(i)}
                \right)^2}{L_k - \mu^{(i)}} 
                -
                \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} 
                \frac{\left(
                    L_k\alpha_k - \mu^{(i)}
                \right)^2}{L_k - \mu^{(i)}} 
                -
                \frac{L_k\alpha_k(\alpha_k - \mu/L_k)}{2} 
                \frac{\left(
                    L_k\alpha_k - \mu^{(i)}
                \right)^2}{L_k - \mu^{(i)}} 
                - \frac{L_k\alpha_k(\alpha_k - \mu^{(i)}/L_k)}{2}
                + \frac{L_k\alpha_k(\alpha_k - \mu^{(i)}/L_k)}{2} 
                - \frac{L_k\alpha_k(\alpha_k - \mu/L_k)}{2} 
                \frac{\left(
                    L_k\alpha_k - \mu^{(i)}
                \right)^2}{L_k - \mu^{(i)}} 
                - \frac{\alpha_k(L_k\alpha_k - \mu^{(i)})}{2}
                + \frac{L_k\alpha_k}{2}
                \frac{\left(
                    \mu - \mu^{(i)}
                \right)}{L_k}
